\chapter{Introduction}
\pagenumbering{arabic}\hspace{3mm}
    The project involves writing formal specification of hardware, and using proof assistant to
formally verify the correctness of the implementation of the same. In computer science formal specification
is the act of proving or disproving correctness of indented algorithms underlying a system with respect to a 
certain formal specification property using formal methods of mathematics. And here we intend to write a tool
that can formally verify hardware properties and generate source code for the same.

\section{Coq -  proof assistant}
    Here for writing specifications and proof for the same specifications we use a proof assistant called
Coq, Coq is an interactive theorem prover. It allows the expression of mathematical assertions , mechanically
checks the proof for these assertions, helps to find formal proofs and extracts a certified program from the
constructive proof of it's formal specification. official website: \href{https://coq.inria.fr/}{Coq official site}

\section{VHDL -  the current target language}
    Currently the target language is set to be VHDL. The candidates for this were initially VHDL , Verilog
and BlueSpec but due to licensing and certain other issues it is decided that the verifier will target VHDL


\section{Organization of The Report}
    The report will be divided into sections that will guide through the materials required for implementation
of the project. As for both specifications and proving the correctness of the specifications we need a proof assistant
and Coq is used here to serve the purpose. but to understand the working of Coq, one should know curry-howard
correspondence and also the use of dependent types for programs that detects most of the errors during compile time.
Throughout this report first Introduction to curry-howard correspondence will be given and then use of dependent typed
languages and finally with an introduction to Coq. 